HETDEX Paper

### 2015-06-02 ms.tex
finished? oii section

\section{RESULTS}

@@

\begin{figure*} 
	\includegraphics[width=\textwidth]{fullKnowledge.pdf} 
	\caption{Intrinsic cluster properties versus the recovered cluster properties for 16758 unique halos comprised of 657916 individual galaxies. The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass. In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.} 
	\label{fig:full} 
\end{figure*}

@@

\begin{figure*} 
	\includegraphics[width=\textwidth]{hetdexDepth.pdf} 
	\caption{HETDEX DEPTH! Intrinsic cluster properties versus the recovered cluster properties for 14239 unique halos comprised of 87754 individual galaxies. The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass. In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.} 
	\label{fig:hetdexDepth} 
\end{figure*}

\subsubsection{\ion{O}{ii} Luminosity}
HETDEX is designed to detect Lyman-$\alpha$ at redshift two. That allows us to detect \ion{O}{ii} emitters to $z\sim 0.49$. The catalog does not provide \ion{O}{ii} luminosities so we must assign them empirically. We use 177107 galaxies from the Sloan Digital Sky Survey (SDSS) Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$. Galaxies are selected which have no redshift warning and have an \ion{O}{ii} flux five times greater than the \ion{O}{ii} flux error.

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
	\caption{686184 $z<0.2$ galaxies} \label{fig:oii sdss} 
\end{figure}

We place each SDSS galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}. To assign an \ion{O}{ii} luminosity to each galaxy in our catalog we place the galaxies on the same and select all SDSS galaxies in a small 2D bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their \ion{O}{ii} luminosities. Using a slice sampling technique we assign the catalog galaxy an \ion{O}{ii} luminosity based on the distribution of SDSS galaxies extracted.

\begin{figure}
	\includegraphics[width=0.49\textwidth]{clustersCMD.pdf}
	\caption{657916 galaxies}
	\label{fig:oii clusters}
\end{figure}

For catalog galaxies which are placed on the CMD near no, or very few ($n<3$) galaxies we assign it zero \ion{O}{ii} luminosity or the mean luminosity, respectively.

\begin{eqnarray}
	g_{DES} = g_{SDSS} - 0.104*(g-r)_{SDSS} + 0.01 \\
	r_{DES} = r_{SDSS} - 0.102*(g-r)_{SDSS} + 0.02
\end{eqnarray}

>>>>

\section{ {\rm[\ion{O}{ii}]} Luminosity}
HETDEX is designed to detect Lyman-$\alpha$ at redshift two. That allows us to detect [\ion{O}{ii}] ($\lambda\lambda 3727-3729\AAA$ doublet) emitters to $z\sim 0.49$. The catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically. We use 503113 galaxies from the Sloan Digital Sky Survey (SDSS) Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected which have no redshift warning.

\begin{figure*} 
	\includegraphics[width=\textwidth]{oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss} 
\end{figure*}

While the difference is small, we convert each SDSS galaxy's observed magnitude to a similar DES magnitude using
\begin{eqnarray}
	g_{DES} = g_{SDSS} - 0.104(g-r)_{SDSS} + 0.01 \\
	r_{DES} = r_{SDSS} - 0.102(g-r)_{SDSS} + 0.02
\end{eqnarray}
from \cite{Bechtol2015} and place each on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}. To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted. For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.

The right panel of Figure~\ref{fig:oii sdss} shows the CMD of all SDSS galaxies. Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by two colored boxes. The histograms show in the Figure's left panel shows the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin. We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.

\section{RESULTS}
Our results section is broken into two large sections. First we analyze our ability to recover cluster parameters from an observing strategy similar to that of HETDEX. In the second Section, we apply observational limits, similar to those expected to apply, and investigate how the parameter recovery improves (or worsens) under those conditions.

@@

\subsubsection{Dynamical Properties}
\begin{figure*} 
	\includegraphics[width=\textwidth]{fullKnowledge.pdf} 
	\caption{Intrinsic cluster properties versus the recovered cluster properties for 16758 unique halos comprised of 657916 individual galaxies. The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass. In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.} 
	\label{fig:full} 
\end{figure*}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsubsection{Structural Properties}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\subsubsection{Dynamical Properties}
\begin{figure*} 
	\includegraphics[width=\textwidth]{hetdexDepth.pdf} 
	\caption{HETDEX DEPTH! Intrinsic cluster properties versus the recovered cluster properties for 14239 unique halos comprised of 87754 individual galaxies. The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass. In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.} 
	\label{fig:hetdexDepth} 
\end{figure*}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsubsection{Structural Properties}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
